Diversification of Australian blind snakes

### 2022-12-14 manuscript.Rmd
modify result

The largest source of outward dispersal is the tropical grassland biome (16.2 ± 4.9 events; 43.6%), which makes up almost double the number of outward dispersals from the arid biome (9.7 ± 3.2 events; 26.0%) (\@ref(fig:fig-biogeobears))c-d. Together the tropical grassland biome and the arid biome contributes the largest source of diversification accounting for 69.6% of outward transitions. On the other hand, the largest sink for all inward dispersals are the temperate grassland biome (7.9 ± 4.2 events; 21.2%) and the mediterranean biome (7.0 ± 2.9 events; 18.8%). The greatest directional transition is from the arid biome to the mediterranean biome (5.3 ± 1.5 events) and from the tropical grassland into the temperate forest biome (5.1 ± 1.3 events) (\@ref(fig:fig-biogeobears)c-d.

>>>>

The largest source of outward dispersal is the tropical grassland biome (16.2 ± 4.9 events; 43.6%), which makes up almost double the number of outward dispersals from the arid biome (9.7 ± 3.2 events; 26.0%) (\@ref(fig:fig-biogeobears))c-d. Together the tropical grassland biome and the arid biome contributes the largest source of diversification accounting for 69.6% of outward transitions. On the other hand, the largest sink for all inward dispersals are the tropical forest biome (7.9 ± 4.2 events; 21.2%) and the mediterranean biome (7.0 ± 2.9 events; 18.8%). The greatest directional transition is from the arid biome to the mediterranean biome (5.3 ± 1.5 events) and from the tropical grassland into the temperate forest biome (5.1 ± 1.3 events) (\@ref(fig:fig-biogeobears)c-d.
